Concurrent Programming with CXL

### 2020-06-07 book/paper.tex
Latest

While spinlocks suffer from starvation, it is a uniform random
process and each process has an equal chance of entering the critical
section.  Thus the probability of starvation is exponentially vanishing.
Unfortunately, such is not the case for the
reader/writer solution of Figure~\ref{fig:rw2lock}.
Consider this scenario: there are two readers and one writer.  One reader
is in the critical section while the writer is waiting.  Now the
second reader tries to enter and is able to.  The first reader leaves.
We are now in a similar situation as the initial state with one reader
in the critical section and the writer waiting, but it is not the same
reader.  Unfortunately for the writer, this scenario can repeat itself
indefinitely.  So even if neither reader was in the critical section
all of the time, and the second reader arrived well after the writer,
the writer never had a chance.
In this chapter, we will present a version of a reader/writer lock
implementation that solves this type of starvation, but won't eliminate
the type of starvation that comes with spinlocks.

>>>>

While spinlocks suffer from starvation, it is a uniform random
process and each process has an equal chance of entering the critical
section.  Thus the probability of starvation is exponentially vanishing.
Unfortunately, such is not the case for the
reader/writer solutions that we presented thus far.
Consider this scenario: there are two readers and one writer.  One reader
is in the critical section while the writer is waiting.  Now the
second reader tries to enter and is able to.  The first reader leaves.
We are now in a similar situation as the initial state with one reader
in the critical section and the writer waiting, but it is not the same
reader.  Unfortunately for the writer, this scenario can repeat itself
indefinitely.  So even if neither reader was in the critical section
all of the time, and the second reader arrived well after the writer,
the writer never had a chance.
In this chapter, we will present a version of a reader/writer lock
implementation that solves this type of starvation, but won't eliminate
the type of starvation.
